Report for Tissue-Specific Proteins

### 2021-08-05 Tissue Specific Report.Rmd
Code finished - needs writing

# Data Input
#setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")
protein_brain = read.csv("Brain_WGCNA.csv")
secreted_protein_brain = read.csv("Secreted_Brain.csv")
ts_protein_brain = read.csv("TissueSpecific_Protein_Brain.csv")
protein_liver = read.csv("Liver_WGCNA.csv")
secreted_protein_liver = read.csv("Secreted_Liver.csv")
ts_protein_liver = read.csv("TissueSpecific_Protein_Liver.csv")

############## Calculate R squared for tissue specific and not tissue specific########################
fin.r.squared_brain = read.csv("R_Squared_Brain.csv")
fin.r.squared_brain_sec = read.csv("R_Squared_Brain_Sec.csv")
fin.r.squared_liver = read.csv("R_Squared_Liver.csv")
fin.r.squared_liver_sec = read.csv("R_Squared_Liver_Sec.csv")
fin.r.squared_brain_notsec = read.csv("R_Squared_Brain_NotSec.csv")
fin.r.squared_liver_notsec = read.csv("R_Squared_Liver_NotSec.csv")

@@

protein_brain = fix.read.csv(protein_brain)
secreted_protein_brain = fix.read.csv(secreted_protein_brain)
ts_protein_brain = fix.read.csv(ts_protein_brain)

protein_liver = fix.read.csv(protein_liver)
secreted_protein_liver = fix.read.csv(secreted_protein_liver)
ts_protein_liver = fix.read.csv(ts_protein_liver)

fin.r.squared_brain = fix.read.csv(fin.r.squared_brain)
fin.r.squared_brain_sec = fix.read.csv(fin.r.squared_brain_sec)
fin.r.squared_liver = fix.read.csv(fin.r.squared_liver)
fin.r.squared_liver_sec = fix.read.csv(fin.r.squared_liver_sec)
fin.r.squared_brain_notsec = fix.read.csv(fin.r.squared_brain_notsec)
fin.r.squared_liver_notsec = fix.read.csv(fin.r.squared_liver_notsec)

@@

ngenes.l = ncol(protein_liver)
ngenes_sec.l = ncol(secreted_protein_liver)
ngenes_ts.l = ncol(ts_protein_liver)
tot_sec = 1760 # from secreted uniprot data
tot_ts = "WHAT"

@@

## THis isn't right...

@@

>>>>

# Data Input
#setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")
protein_brain = read.csv("Brain_WGCNA.csv")
secreted_protein_brain = read.csv("Secreted_Brain.csv")
#ts_protein_brain = read.csv("TissueSpecific_Protein_Brain.csv")
protein_liver = read.csv("Liver_WGCNA.csv")
secreted_protein_liver = read.csv("Secreted_Liver.csv")
#ts_protein_liver = read.csv("TissueSpecific_Protein_Liver.csv")

fin.r.squared_brain = read.csv("R_Squared_Brain.csv")
fin.r.squared_liver = read.csv("R_Squared_Liver.csv")

@@

protein_brain = fix.read.csv(protein_brain)
secreted_protein_brain = fix.read.csv(secreted_protein_brain)
#ts_protein_brain = fix.read.csv(ts_protein_brain)

protein_liver = fix.read.csv(protein_liver)
secreted_protein_liver = fix.read.csv(secreted_protein_liver)
#ts_protein_liver = fix.read.csv(ts_protein_liver)

fin.r.squared_brain = fix.read.csv(fin.r.squared_brain)
fin.r.squared_liver = fix.read.csv(fin.r.squared_liver)

```{r}
# looking for unique genes

genes_brain = colnames(secreted_protein_brain)
genes_liver = colnames(secreted_protein_liver)

gee = genes_brain %in% genes_liver
gee = gee == FALSE
only_brain = genes_brain[gee]

wee = genes_liver %in% genes_brain
wee = wee == FALSE
only_liver = genes_liver[wee]

ts_protein_brain = secreted_protein_brain[, colnames(secreted_protein_brain) %in% only_brain]
ts_protein_liver = secreted_protein_liver[, colnames(secreted_protein_liver) %in% only_liver]

setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")
write.csv(ts_protein_brain, "TissueSpecific2_Protein_Brain.csv")
write.csv(ts_protein_liver, "TissueSpecific2_Protein_Liver.csv")

@@

ngenes.l = ncol(protein_liver)
ngenes_sec.l = ncol(secreted_protein_liver)
ngenes_ts.l = ncol(ts_protein_liver)
tot_sec = 1760 # from secreted uniprot data
tot_ts = ngenes_ts + ngenes_ts.l

@@

@@

```{r}
# R squared

rsq.brain = sub(" ~ strain_factor_brain.*", "", fin.r.squared_brain$names_brain)
rsq.liver = sub(" ~ strain_factor_liver.*", "", fin.r.squared_liver$names_liver)

fin.r.squared_brain[,1] = rsq.brain
fin.r.squared_liver[,1] = rsq.liver

r.squared_brain_ts = fin.r.squared_brain[fin.r.squared_brain$names_brain %in% colnames(ts_protein_brain),]
r.squared_liver_ts = fin.r.squared_liver[fin.r.squared_liver$names_liver %in% colnames(ts_protein_liver),]

r.squared_brain_notts = fin.r.squared_brain[!(fin.r.squared_brain$names_brain %in% colnames(ts_protein_brain)),]
r.squared_liver_notts = fin.r.squared_liver[!(fin.r.squared_liver$names_liver %in% colnames(ts_protein_liver)),]

#brain

gee = cbind(rep("not ts", times = dim(r.squared_brain_notts)[1]), r.squared_brain_notts[,2])
gee2 = cbind(rep("ts", times = dim(r.squared_brain_ts)[1]), r.squared_brain_ts[,2])

wil.b = rbind(gee, gee2)
wil.b = as.data.frame(wil.b)
colnames(wil.b) = c("trt", "r.sq")

wil.b$trt = as.factor(wil.b$trt)
wil.b$r.sq = as.numeric(wil.b$r.sq)

wil.brain = coin::wilcox_test(r.sq ~ trt, wil.b)

# liver

gee = cbind(rep("not ts", times = dim(r.squared_liver_notts)[1]), r.squared_liver_notts[,2])
gee2 = cbind(rep("ts", times = dim(r.squared_liver_ts)[1]), r.squared_liver_ts[,2])

wil.l = rbind(gee, gee2)
wil.l = as.data.frame(wil.l)
colnames(wil.l) = c("trt", "r.sq")

wil.l$trt = as.factor(wil.l$trt)
wil.l$r.sq = as.numeric(wil.l$r.sq)

wil.liver = coin::wilcox_test(r.sq ~ trt, wil.l)

```{r}

# Density R Squared

ggplot(wil.b, aes(x = r.sq, color = trt)) + 
  geom_density() +
  labs(title="R Squared Density Curve: Brain",x="R Squared", y = "Density")

ggplot(wil.l, aes(x = r.sq, color = trt)) + 
  geom_density() +
  labs(title="R Squared Density Curve: Liver",x="R Squared", y = "Density")

# Box R Squared

boxplot(fin.r.squared_brain[,2], fin.r.squared_brain_sec[,2], names = c("Not TS", "TS"), xlab = "R Squared", main = "R Squared Brain Data")
boxplot(fin.r.squared_liver[,2], fin.r.squared_liver_sec[,2], names = c("Not TS", "TS"), xlab = "R Squared", main = "R Squared Liver Data")
